### 2023-03-30 manuscript.Rmd
WHEW GRAPHS

```{r setup, include = FALSE}
library(papaja)
library(lavaan)
```

@@

```{r}
model.1 <- "lv =~ q1 + q2 + q3 + q4 + q5"

>>>>

```{r setup, include = FALSE}
library(papaja)
library(lavaan)
library(broom)
library(dplyr)
library(ggplot2)
# devtools::install_github("psyteachr/introdataviz")
library(introdataviz)

# CFA function
mgcfa <- function(data, group, model){

  group_names <- unique(data[ , group])

  model.overall <- cfa(model = model, data = data)
  model.group1 <- cfa(model = model, data = subset(data, group == group_names[1]))
  model.group2 <- cfa(model = model, data = subset(data, group == group_names[2]))
  model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
  model.metric <- cfa(model = model, data = data, group = group, group.equal = "loadings")
  model.scalar <- cfa(model = model, data = data, group = group, group.equal = c("loadings", "intercepts"))
  model.strict <- cfa(model = model, data = data, group = group, group.equal =  c("loadings", "intercepts", "residuals"))

  model_coef <- bind_rows(
    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
  )

  model_fit <- bind_rows(
    glance(model.overall) %>% mutate(model = "overall"), 
    glance(model.group1) %>% mutate(model = "group1"), 
    glance(model.group2) %>% mutate(model = "group2"), 
    glance(model.configural) %>% mutate(model = "configural"), 
    glance(model.metric) %>% mutate(model = "metric"), 
    glance(model.scalar) %>% mutate(model = "scalar"), 
    glance(model.strict) %>% mutate(model = "strict")
    )

  return(list(
    "model_coef" = model_coef,
    "model_fit" = model_fit
  ))

}
```

@@

```{r create-data}
library(lavaan)

# build invariant model one factor
model.invariant.g1 <- "lv =~ .9*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5"
model.invariant.g2 <- "lv =~ .87*q1 + .43*q2 + .54*q3 + .4*q4 + .61*q5"
model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5"

# simulate data
df.invariant <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa") %>% 
    mutate(group = "Group 1"), 
  simulateData(model.invariant.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa") %>% 
    mutate(group = "Group 2") 
)

```{r run-cfa}
# invariant CFA
results.invariant <- mgcfa(df.invariant, "group", model.overall)
```

```{r invariant-picture}
graph.data <- results.invariant$model_coef %>% # put in tidy coefficients
  filter(model == "configural") %>% # pick a model
  filter(grepl("q4", term)) %>%  # pick a question
  mutate(group = factor(group, levels = c(1,2), labels = c("Group 1", "Group 2")))

graph.data$low <- graph.data$estimate - 2*graph.data$estimate
graph.data$high <- graph.data$estimate + 2*graph.data$estimate

# X = latent variable (so interpretation is z-score)
# Y = observed variable
# set x and y limits
x_limits <- c(-1,1)
y_limits <- c(min(df.invariant$q4), max(df.invariant$q4))

# make ribbon data y = slope*x + intercept
ribbondata <- bind_rows(
  data.frame(
  x = seq(from = x_limits[1] - 1,  
          to = x_limits[2] + 1, 
          by = .05), 
  group = unique(graph.data$group)[1]
) %>% 
  mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
               slice_head() %>% pull(estimate) * x) - 
           (2*graph.data %>% filter(op == "=~") %>% 
                  slice_head() %>% pull(std.error)) +
           graph.data %>% filter(op == "~1") %>% 
               slice_head() %>% pull(estimate), 
         ymax = (graph.data %>% filter(op == "=~") %>% 
               slice_head() %>% pull(estimate) * x) + 
           (2*graph.data %>% filter(op == "=~") %>% 
                  slice_head() %>% pull(std.error)) +
           graph.data %>% filter(op == "~1") %>% 
               slice_head() %>% pull(estimate)), 
  data.frame(
    x = seq(from = x_limits[1] - 1,  
            to = x_limits[2] + 1, 
            by = .05), 
    group = unique(graph.data$group)[2]
  ) %>% 
    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
                 slice_tail() %>% pull(estimate) * x) - 
             (2*graph.data %>% filter(op == "=~") %>% 
                    slice_tail() %>% pull(std.error)) +
             graph.data %>% filter(op == "~1") %>% 
                 slice_tail() %>% pull(estimate), 
           ymax = (graph.data %>% filter(op == "=~") %>% 
                 slice_tail() %>% pull(estimate) * x) + 
             (2*graph.data %>% filter(op == "=~") %>% 
                    slice_tail() %>% pull(std.error)) +
             graph.data %>% filter(op == "~1") %>% 
                 slice_tail() %>% pull(estimate))
)

pointdata <- data.frame(
  x = c(0,0),
  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
  group = graph.data %>% filter(op == "~1") %>% pull(group),
  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
    2 * graph.data %>% filter(op == "~1") %>% pull(std.error), 
  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
    2 * graph.data %>% filter(op == "~1") %>% pull(std.error)
)

linedata <- data.frame(
  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
  group = graph.data %>% filter(op == "~1") %>% pull(group)
)

violindata <- data.frame(
  y = c(rnorm(n = 1000, 
            mean = graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(estimate), 
            sd = graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(std.error)), 
        rnorm(n = 1000, 
            mean = graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(estimate), 
            sd = graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(std.error))),
  group = c(rep(graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(group), 100),
            rep(graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(group), 100)), 
  x = 1
)

latent_means <- data.frame(
  predict(model.overall.model), 
  group = df.invariant$group
)

variance_plot <- 
  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
  geom_split_violin() + 
  theme_void() + 
  theme(legend.position = "none") + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "black")

intercept_plot <- 
  ggplot() + 
  # basic set up
  theme_classic() + 
  xlab("Latent Variable") + 
  ylab("Observed Variable") + 
  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
  # plot the intercepts 
  geom_point(data = pointdata, 
             aes(x = x, y = y, color = group), 
             inherit.aes = FALSE) + 
  geom_errorbar(data = pointdata,
                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
                inherit.aes = FALSE, width = .10) + 
  # plot the slopes
  geom_abline(data = linedata,
              aes(slope = slope, intercept = intercept, color = group)) + 
  geom_ribbon(data = ribbondata, 
              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
              inherit.aes = FALSE, alpha = .2) + 
  scale_color_discrete(name = "Group") + 
  scale_fill_discrete(name = "Group") + 
  geom_vline(xintercept = 0)

# latent means
mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
  geom_density(alpha = .2) + 
  theme_classic() + 
  xlab("Latent Variable") + 
  ylab("Density") + 
  geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
             aes(xintercept = mean, color = group)) + 
  theme(legend.position = "none") 
```

```{r}
